What We Eval in the Shadows

### 2021-04-14 paper/main.tex
minro

The environment in which evaluation happens determines what is visible to the
computation started by \eval, and the potential reach of its side-effects. The
second argument to \eval is used to specify that environment. We propose the
following high-level classification:

>>>>

The environment in which evaluation happens determines what is visible to the
computation started by \eval and the potential reach of its side-effects. The
second argument to \eval specifies that environment. We propose the
following high-level classification the environments of \eval:
